Title Goes Here

### 2020-03-19 analysis/paper/paper.Rmd
tried CV and pearson's r

library(CTtps) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory
```

@@

```

>>>>

#library(CTtps) # Or use devtools::load_all('.', quiet = T) if your code is in script files, rather than as functions in the `/R` diretory

library(here)
```

@@

# Correlations with significance levels
library(Hmisc)
rcorr(ML,BL, type = "pearson") # type can be pearson or spearman

# Coefficient of variation (CV)
library(goeveg)
CV_ML <- cv(ML, na.rm = FALSE) #na.rm: logical. Should missing values be removed?
CV_BL <- cv(BL, na.rm = FALSE)

plot(CV_ML, CV_BL)
```
